<small> Supplementary materials for the main submission entitled - <br><br> Clustering time series based on probability distributions across temporal granularities

### 2021-11-15 paper-supplementary.Rmd
supplementary update

```{r external, include = FALSE, cache = FALSE}
knitr::read_chunk('script/main.R')
read_chunk(here::here("validation/simdata01.R"))
knitr::read_chunk('script/gracsr-supplementary.R')
```

>>>>

```{r external, include = FALSE, cache = FALSE}
knitr::read_chunk('script/mylibrary.R')
knitr::read_chunk('script/mytheme.R')
knitr::read_chunk('script/validation.R')
read_chunk(here::here("validation/simdata01.R"))
knitr::read_chunk('script/supplementary.R')
```
